%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------    
\cventry
    {MS in Computer Science end Engineering}
    {Politecnico di Milano}
    {Milano, Italia}
    {Sep. 2018 -- Present}
    {Current average: 27.67 / 30}
    
\cventry
    {BS in Ingegneria Informatica}
    {Politecnico di Milano}
    {Milano, Italia}
    {Sep. 2015 -- Sep. 2018}
    {Final mark: 100 / 110}
    
\cventry
    {High School}
    {Liceo Scientifico Statale Elio Vittorini}
    {Milano, Italia}
    {Sep. 2010 -- Jun. 2015}
    {Final mark: 100 / 100}
%---------------------------------------------------------
\end{cventries}

%\vspace{1em}
\cvsection{Projects}

\begin{cventries}
    
\cventry
    {Design and Implementation of Mobile Applications}
    {iOS Application}
    {Ongoing}
    {}
    {Design and implementation of a mobile application for tourists. This project is being developed in collaboration with \textit{Bending Spoons}.}
    
\cventry
    {Middleware Technologies for Distributed Systems}
    {Temperature WSN}
    {Ongoing}
    {}
    {Implementation and simulation of a multi-hop Wireless Sensor Network using TinyOS.}
    
\cventry
    {Hypermedia Applications}
    {Website}
    {Ongoing}
    {}
    {Design and implementation of a website for a voluntary association.}

\iffalse
\cventry
    {Recommender System}
    {Kaggle competition}
    {}
    {}
    {Design and implementation of a system able to recommend relevant items to users of an e-commerce website. \href{https://github.com/Alenichel/CodiglioniNichelini\_recsys-polimi-2019}{https://github.com/Alenichel/CodiglioniNichelini\_recsys-polimi-2019}}
\fi
    
\cventry
    {Advanced Operating Systems}
    {BarbequeueRTRM}
    {}
    {}
    {Implementation using Google Protocol Buffer of the inter-process communication layer of a runtime resource manager. \href{https://github.com/fabiocody/AOS\_Project/tree/protobuf}{https://github.com/fabiocody/AOS\_Project/tree/protobuf}}
    
\cventry
    {Internet of Things}
    {Smart bins}
    {}
    {}
    {Implementation and simulation of a smart bins system using Contiki. \qquad\qquad\qquad\qquad\qquad\qquad\href{https://github.com/fabiocody/CodiglioniNicheliniIoT}{https://github.com/fabiocody/CodiglioniNicheliniIoT}}
    
\cventry
    {Software Engineering}
    {Sagrada}
    {}
    {}
    {Implementation of a videogame in Java, using JavaFX and RMI. \qquad\qquad\qquad\qquad\qquad\qquad\qquad\href{https://github.com/fabiocody/ProgettoIngSwFLK}{https://github.com/fabiocody/ProgettoIngSwFLK}}
    
    
\end{cventries}


